---
title: "R Project 1 - Hello R"
author: "Ayrton Wafo"
date: "Due Fed 3rd"
output: 
  html_document: 
    fig_width: 5
    fig_height: 7
    highlight: haddock
    theme: journal
---

MAKE SURE YOU READ AND FOLLOW **ALL** INSTRUCTIONS ON THE INSTRUCTION DOCUMENT. 

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

The datasaurus_dozen data frame contain 1846 rows and 3 columns.
Variables included in the data frame are: dataset, x and y.

### Exercise 2

First let's plot the data in the dino dataset:

```{r plot-dino, fig.height=4, fig.width=4}
#filter dino data set
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
#plot dino data set
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
#correlation
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

let's filter in star dataset and plot the data:

```{r plot-star,fig.height=4, fig.width=4}
#filter star data set
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")
#plot star data set
ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()

```

And next calculate the correlation between `x` and `y` in the star dataset:
 
```{r cor-star}
#correlation between x and y
star_data %>%
  summarize(r = cor(x, y))

```
The value (r of star) is greater than r of dino.

### Exercise 4

let's filter in circle dataset and plot the data:

```{r plot-circle,fig.height=4, fig.width=4}
#filter circle data set
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
#plot circle data set
ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()

```


And next calculate the correlation between `x` and `y` in the circle dataset:
 
```{r cor-circle}
#correlation between x and y
circle_data %>%
  summarize(r = cor(x, y))

```
The value (r of circle) is less than r of dino.

### Exercise 5

let’s plot all datasets at once using facetting

```{r plot-datasets,fig.height=7, fig.width=8}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+
geom_point()+
facet_wrap(~ dataset, ncol = 3) + # facet the dataset variable, in 3 cols
theme(legend.position = "none")

```

And next calculate the correlation between `x` and `y` in the dataset:

```{r cor-datasets}
datasaurus_dozen %>%
group_by(dataset) %>%
summarize(r = cor(x, y)) %>%
print(13)
```
